Bob Simulation Sugestion

### 2023-01-18 graphs_newt_snakes/bob_notes.Rmd
I have updated the results for the last set of experiments. Tomorrow I will need to spend some time reviewing them.

---
title: "Moving Together"
output: html_document
date: '2023-01-10'
---
```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

@@

both_lower_w_no_exp_cor<- read.csv("~/Desktop/both_lower_w_no_exp/all_cor.txt" , header = TRUE)
both_lower_w_no_exp_cor$group_rep <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd, "_", both_lower_w_no_exp_cor$rep)
both_lower_w_no_exp_cor$group <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd)
both_lower_w_no_exp_cor$sim=LETTERS[factor(both_lower_w_no_exp_cor$group)]

@@

lower_w_cor<- read.csv("~/Desktop/lower_w/all_cor.txt" , header = TRUE)
lower_w_cor$group_rep <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd, "_", lower_w_cor$rep)
lower_w_cor$group <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd)
lower_w_cor$sim=LETTERS[factor(lower_w_cor$group)]

@@

no_exp_cor<- read.csv("~/Desktop/no_exp/all_cor.txt" , header = TRUE)
no_exp_cor$group_rep <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd, "_", no_exp_cor$rep)
no_exp_cor$group <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd)
no_exp_cor$sim=LETTERS[factor(no_exp_cor$group)]

@@

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

@@

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

return(my_plot)
}
GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

@@

params<-create_parm_file(file, min_gen, max_gen)

my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

@@

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)

@@

### Phenotype differences (lower_wp)
```{r, whale lw}
min_gen=5000
max_gen=10000
rep=1

whale_gen(lower_wp_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (lower_wp)
```{r, popsize and pheno lw}

suppressMessages(print(two_hist(lower_wp_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

@@

## Correlation{.tabset}
HEREREERERERER
### cor (both_lower_w_no_exp)
```{r, combo myplots}

@@

```{r, red in grid files}
require(readr)
both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
both_lower_w_no_exp_grid$grid_num = 5

```{r, red in grid files lw}
require(readr)
lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
lower_w_grid$grid_num = 5

```{r, red in grid files ne}
require(readr)
no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000))
no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
no_exp_grid$grid_num = 5

## What is up with the correlations

## Early Simulation Correlation (both_lower_w_no_exp)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

## Early Simulation Correlation (lower_w)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

## Early Simulation Correlation (no_exp)  {.tabset}

### Mean 
```{r, cor grid high cor mean}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### popsize
```{r, cor grid high cor popsize}

file=no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=9501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

```{r, red in grid files 2}
require(readr)
both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep)
both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd)
both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)]
both_lower_w_no_exp_grid$grid_num = 5

```{r, red in grid files 2 lw}
require(readr)
lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep)
lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd)
lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)]
lower_w_grid$grid_num = 5

```{r, red in grid files 2 ne}
require(readr)
no_exp_grid<- read.csv("~/Desktop/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000))
no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep)
no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd)
no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)]
no_exp_grid$grid_num = 5

## Late Simulation Correlation (both_lower_w_no_exp) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=both_lower_w_no_exp_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

## Late Simulation Correlation (lower_w) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="mean"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Max 
```{r, cor grid high cor max late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="max"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Min 
```{r, cor grid high cor min late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="min"
row_num=20
col_num=5

grid_plot(file_name, spegen, file, type, row_num, col_num)
```

### Pop size
```{r, cor grid high cor popsize late}

file=lower_w_grid
file_name="1e-11_5_1e-10_0.5_0"
spegen=44501
type="num_ind"
row_num=20
col_num=5
grid_plot(file_name, spegen, file, type, row_num, col_num)

## Late Simulation Correlation (no_exp) {.tabset}

### Mean 
```{r, cor grid high cor mean late}

>>>>

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE, message = FALSE,echo = FALSE)

@@

both_lower_w_no_exp_cor<- read.csv("~/Desktop/bob_suggestion/both_lower_w_no_exp/all_cor.txt" , header = TRUE)
both_lower_w_no_exp_cor$group_rep <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd, "_", both_lower_w_no_exp_cor$rep)
both_lower_w_no_exp_cor$group <- paste0(both_lower_w_no_exp_cor$snake_mu_rate, "_", both_lower_w_no_exp_cor$snake_mu_effect_sd,"_",both_lower_w_no_exp_cor$newt_mu_rate, "_", both_lower_w_no_exp_cor$newt_mu_effect_sd)
both_lower_w_no_exp_cor$sim=LETTERS[factor(both_lower_w_no_exp_cor$group)]

@@

lower_w_cor<- read.csv("~/Desktop/bob_suggestion/lower_w/all_cor.txt" , header = TRUE)
lower_w_cor$group_rep <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd, "_", lower_w_cor$rep)
lower_w_cor$group <- paste0(lower_w_cor$snake_mu_rate, "_", lower_w_cor$snake_mu_effect_sd,"_",lower_w_cor$newt_mu_rate, "_", lower_w_cor$newt_mu_effect_sd)
lower_w_cor$sim=LETTERS[factor(lower_w_cor$group)]

@@

no_exp_cor<- read.csv("~/Desktop/bob_suggestion/no_exp/all_cor.txt" , header = TRUE)
no_exp_cor$group_rep <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd, "_", no_exp_cor$rep)
no_exp_cor$group <- paste0(no_exp_cor$snake_mu_rate, "_", no_exp_cor$snake_mu_effect_sd,"_",no_exp_cor$newt_mu_rate, "_", no_exp_cor$newt_mu_effect_sd)
no_exp_cor$sim=LETTERS[factor(no_exp_cor$group)]

@@

 create_parm_file_nc <- function(file, min_gen, max_gen){

   file$test_factor <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)

params <- data_frame()

for(i in 1:length(unique(file$test_factor))){

  pattern=unique(file$test_factor)[i]

  sumitup <- file[which(file$gen>=min_gen & file$gen<=max_gen & file$test_factor ==pattern),]

  params_temp<- data_frame(Newt_mean_Pheno=mean(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno=mean(sumitup$Snake_mean_Pheno), 
                           Newt_mean_Pheno_sd=sd(sumitup$Newt_mean_Pheno),
                           Snake_mean_Pheno_sd=sd(sumitup$Snake_mean_Pheno),
                           Newt_pop_size=mean(sumitup$Newt_pop_size),
                           Snake_pop_size=mean(sumitup$Snake_pop_size),
                           dif=mean(sumitup$dif),
                           snake_mu_rate=unlist(strsplit(pattern, "_"))[2],
                           newt_mu_rate=unlist(strsplit(pattern, "_"))[4],
                           snake_mu_effect_sd=unlist(strsplit(pattern, "_"))[3],
                           newt_mu_effect_sd=unlist(strsplit(pattern, "_"))[5],
                           rep=unlist(strsplit(pattern, "_"))[6],
                           test_factor=pattern)

GA_summary <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label ){

@@

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=as.numeric(get(x_line)), y=as.numeric(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

GA_summary_by_species <- function(file, min_gen, max_gen, x_line, y_line, title, subt, y_label, x_label){

@@

params<-create_parm_file(file, min_gen, max_gen)
params = na.omit(params)
my_plot <- ggplot(params) +
  #xlim(0, 1000)+
  ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
  xlab(x_label) + ylab(y_label)+
  geom_point(aes(x=(get(x_line)), y=(get(y_line)), color = factor(snake), shape=factor(newt)),size=3)+
#  geom_point(aes(x=as.numeric(Newt_pop_size_20), y=as.numeric(Snake_pop_size_20), color = factor(snake), shape=factor(newt)))+
  theme(plot.title = element_text(size=5)) +
  #scale_colour_gradient2(high = "steelblue", mid = "beige", low = "darkred")+
  #labs(colour = color_label) +
  #facet_wrap(~sim)+
  theme_bw() +  theme(axis.text.x = element_text( hjust=1, size = 8))

@@

build_heatmap <- function(file, min_gen, max_gen, fill_line, fill_line_text, title, subt, y_label, x_label, red_blue=F){
  file$snake_newt_rep <- paste0(file$snake_mu_rate, "_", file$snake_mu_effect_sd, "_", file$newt_mu_rate, "_", file$newt_mu_effect_sd, "_", file$rep)
  params<-create_parm_file(file, min_gen, max_gen)
  params = na.omit(params)

@@

### Phenotype differences (lower_w)
```{r, whale lw}
min_gen=5000
max_gen=10000
rep=1

whale_gen(lower_w_lit, title="Space: Newt VS Snake Population Size Color=S-N Phenotype", subt="Gen 16sims", y_label="Snake Popsize", x_label="Newt Phenotype", min_gen=min_gen, max_gen=max_gen, rep=rep )
```

### Phenotype & Populationsize differences (lower_w)
```{r, popsize and pheno lw}

suppressMessages(print(two_hist(lower_w_lit, title="Snake-Newt Winning Hist", subt="Gen 16sims", y_label="Count", x_label="Snake-Newt Popsize/1000 (green) & Snake-Newt Phenotype (purple)",  min_gen=min_gen, max_gen=max_gen, rep=rep )))

@@

## Correlation{.tabset}
HEREREERERERER

### cor (both_lower_w_no_exp)
```{r, combo myplots}

@@

<!-- ```{r, red in grid files} -->
<!-- require(readr) -->
<!-- both_lower_w_no_exp_grid<- read.csv("~/Desktop/bob_suggestion/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
<!-- both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep) -->
<!-- both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd) -->
<!-- both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)] -->
<!-- both_lower_w_no_exp_grid$grid_num = 5 -->

<!-- ``` -->

<!-- ```{r, red in grid files lw} -->
<!-- require(readr) -->
<!-- lower_w_grid<- read.csv("~/Desktop/bob_suggestion/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
<!-- lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep) -->
<!-- lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd) -->
<!-- lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)] -->
<!-- lower_w_grid$grid_num = 5 -->

<!-- ``` -->

<!-- ```{r, red in grid files ne} -->
<!-- require(readr) -->
<!-- no_exp_grid<- read.csv("~/Desktop/bob_suggestion/no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 9000, 10000)) -->
<!-- no_exp_grid$group_rep <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd, "_", no_exp_grid$rep) -->
<!-- no_exp_grid$group <- paste0(no_exp_grid$snake_mu_rate, "_", no_exp_grid$snake_mu_effect_sd,"_",no_exp_grid$newt_mu_rate, "_", no_exp_grid$newt_mu_effect_sd) -->
<!-- no_exp_grid$sim=LETTERS[factor(no_exp_grid$group)] -->
<!-- no_exp_grid$grid_num = 5 -->

<!-- ``` -->

<!-- ## What is up with the correlations -->

<!-- ## Early Simulation Correlation (both_lower_w_no_exp)  {.tabset} -->

<!-- ### Mean  -->
<!-- ```{r, cor grid high cor mean} -->

<!-- file=both_lower_w_no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="mean" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Max  -->
<!-- ```{r, cor grid high cor max} -->

<!-- file=both_lower_w_no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="max" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Min  -->
<!-- ```{r, cor grid high cor min} -->

<!-- file=both_lower_w_no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="min" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### popsize -->
<!-- ```{r, cor grid high cor popsize} -->

<!-- file=both_lower_w_no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="num_ind" -->
<!-- row_num=20 -->
<!-- col_num=5 -->
<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->

<!-- ``` -->

<!-- ## {-} -->

<!-- ## Early Simulation Correlation (lower_w)  {.tabset} -->

<!-- ### Mean  -->
<!-- ```{r, cor grid high cor mean lw} -->

<!-- file=lower_w_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="mean" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Max  -->
<!-- ```{r, cor grid high cor max lw} -->

<!-- file=lower_w_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="max" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Min  -->
<!-- ```{r, cor grid high cor min lw} -->

<!-- file=lower_w_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="min" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### popsize -->
<!-- ```{r, cor grid high cor popsize lw} -->

<!-- file=lower_w_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="num_ind" -->
<!-- row_num=20 -->
<!-- col_num=5 -->
<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->

<!-- ``` -->

<!-- ## {-} -->

<!-- ## Early Simulation Correlation (no_exp)  {.tabset} -->

<!-- ### Mean  -->
<!-- ```{r, cor grid high cor mean ne} -->

<!-- file=no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="mean" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Max  -->
<!-- ```{r, cor grid high cor max  ne} -->

<!-- file=no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="max" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### Min  -->
<!-- ```{r, cor grid high cor min ne} -->

<!-- file=no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="min" -->
<!-- row_num=20 -->
<!-- col_num=5 -->

<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->
<!-- ``` -->

<!-- ### popsize -->
<!-- ```{r, cor grid high cor popsize ne} -->

<!-- file=no_exp_grid -->
<!-- file_name="1e-11_5_1e-10_0.5_0" -->
<!-- spegen=9501 -->
<!-- type="num_ind" -->
<!-- row_num=20 -->
<!-- col_num=5 -->
<!-- grid_plot(file_name, spegen, file, type, row_num, col_num) -->

<!-- ``` -->

<!-- ## {-} -->

<!-- ```{r, red in grid files 2} -->
<!-- require(readr) -->
<!-- both_lower_w_no_exp_grid<- read.csv("~/Desktop/both_lower_w_no_exp/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000)) -->
<!-- both_lower_w_no_exp_grid$group_rep <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd, "_", both_lower_w_no_exp_grid$rep) -->
<!-- both_lower_w_no_exp_grid$group <- paste0(both_lower_w_no_exp_grid$snake_mu_rate, "_", both_lower_w_no_exp_grid$snake_mu_effect_sd,"_",both_lower_w_no_exp_grid$newt_mu_rate, "_", both_lower_w_no_exp_grid$newt_mu_effect_sd) -->
<!-- both_lower_w_no_exp_grid$sim=LETTERS[factor(both_lower_w_no_exp_grid$group)] -->
<!-- both_lower_w_no_exp_grid$grid_num = 5 -->

<!-- ``` -->

<!-- ```{r, red in grid files 2 lw} -->
<!-- require(readr) -->
<!-- lower_w_grid<- read.csv("~/Desktop/lower_w/all_grid.txt" , header = TRUE) %>%  filter(between(generation, 40000, 50000)) -->
<!-- lower_w_grid$group_rep <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd, "_", lower_w_grid$rep) -->
<!-- lower_w_grid$group <- paste0(lower_w_grid$snake_mu_rate, "_", lower_w_grid$snake_mu_effect_sd,"_",lower_w_grid$newt_mu_rate, "_", lower_w_grid$newt_mu_effect_sd) -->
<!-- lower_w_grid$sim=LETTERS[factor(lower_w_grid$group)] -->
<!-- lower_w_grid$grid_num = 5 -->

<!-- ``` -->
